%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {California Institute of Technology } % Job title
    {Graduate Student Researcher} % Organization
    {Pasadena, California} % Location
    {Oct. 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Cosmology with gravitational waves, space based gravitational wave detectors, black hole perturbation theory, and testing general relativity with Prof. Yanbei Chen}
        % \item{Measuring cosmological parameters by stacking many dark siren events together, finding that space based detectors can improve results from ground detectors.}
        \item{Studied science that can be achieved with decihertz gravitational wave detectors -- improved cosmological measurements, hierarchical triples, and repeated hierarchical triple lensing.}
        \item{With a model motivated by a quantum gravity, examined how random metric fluctuations near a black hole can cause deviations from general relativity and be optimally detected.}
        \item{Mentored three undergraduates on research projects which are leading to publications: Andrew Laeuger, Agla Þórarinsdóttir, and Chris Jungkind. }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {University of Virginia} % Job title
    {Undergraduate Researcher} % Organization
    {Charlottesville, Virginia} % Location
    {Oct. 2017 - Aug. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        % \item{Astrophysical tests of general relativity }
        \item{Studied how binary pulsars and gravitational waves measurements can constrain deviations from general relativity with Prof. Kent Yagi.}
        \item{Highlighted the potential of testing general relativity using systems like a black hole-pulsar and a hierarchical triple pulsar. }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {LIGO Livingston} % Job title
    {Summer Undergraduate Research Fellow} % Organization
    {Livingston, Louisiana} % Location
    {Jun. 2017 - Aug. 2017 } % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Analyzed angular controls systems noise at LIGO with Dr. Marie Kasprzack, Dr. Adam Mullavey, and Dr. Arnaud Pele.}
      \end{cvitems}
    }

%---------------------------------------------------------
  % \cventry
  %   {James Madison University} % Job title
  %   {Undergraduate Researcher} % Organization
  %   {Harrisonburg, Virginia} % Location
  %   {May. 2015 - Aug. 2016 } % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Analysis of floating soap bubble rheology under normal stress with Klebert Feitosa}
  %     \end{cvitems}
  %   }

%---------------------------------------------------------
\end{cventries}
