%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Presentations}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvpresentations}

%---------------------------------------------------------

    \cvpresentation
    {B. Seymour and Y. Chen. \href{https://meetings.aps.org/Meeting/APR23/Session/C08.9}{“Constraining Nonviolent Nonlocality by Stacking Gravitational Wave Events,”} American Physical Society April Meeting. Sacramento, CA. (Oral)}
    {Apr. 2024}
    
%---------------------------------------------------------

    \cvpresentation
    {B. Seymour and Y. Chen. “Searching for Nonviolent Nonlocality in LIGO,” LIGO-Virgo-Kagra Meeting. Baton Rouge, LA. (Poster)}
    {Mar. 2024}
    
%---------------------------------------------------------

    \cvpresentation
    {B. Seymour and Y. Chen. “Detectability of Nonviolent Nonlocality with LIGO,” 40th Pacific Coast Gravity Meeting. Santa Barbara, CA. (Oral)}
    {Mar. 2024}

%---------------------------------------------------------

    \cvpresentation
    {B. Seymour and Y. Chen. \href{https://meetings.aps.org/Meeting/APR23/Session/C08.9}{“Probing the Effects of Nonviolent Nonlocality with Gravitational Waves,”} American Physical Society April Meeting. Minneapolis, MN. (Oral)}
    {Apr. 2023}
    
%---------------------------------------------------------    

    \cvpresentation
    {B. Seymour and Y. Chen. “Probing the Effects of Nonviolent Nonlocality with Gravitational Waves,” 39th Pacific Coast Gravity Meeting. Pasadena, CA. (Oral)}
    {Mar. 2023}

%---------------------------------------------------------

    \cvpresentation
    {B. Seymour, H. Yu, and Y. Chen. \href{https://meetings.aps.org/Meeting/APR22/Session/Q16.7}{“Multi-band Gravitational Wave Cosmography with Dark Sirens,”} American Physical Society April Meeting. New York, NY. (Oral)}
    {Apr. 2022}
    
%---------------------------------------------------------    

    \cvpresentation
    {B. Seymour, H. Yu, and Y. Chen. “Multi-band Gravitational Wave Cosmography with Dark Sirens,” 38th Pacific Coast Gravity Meeting. Davis, CA. (Oral)}
    {Mar. 2022}

%---------------------------------------------------------

    \cvpresentation
    {B. Seymour, and K. Yagi. \href{https://meetings.aps.org/Meeting/APR19/Session/D16.7}{“Black Hole-Pulsar Binary Tests of Gravity,”} American Physical Society April Meeting. Denver, CO. (Oral)}
    {Apr. 2019}
    
%---------------------------------------------------------
  \cvpresentation
    {B. Seymour, and K. Yagi. "Testing General Relativity with Black Hole-Pulsar Binaries," Society of Physics Students 8th Annual Undergraduate Physics Research Symposium. Charlottesville, VA. (Oral, 2nd place)} % Role
    {Nov. 2018 } % Date(s)
    
%---------------------------------------------------------
  \cvpresentation
    {B. Seymour, and K. Yagi. “Testing General Relativity with Black Hole-Pulsar Binaries,” Gravity Group Meeting. Charlottesville, VA. (Oral)} % Role
    {Nov. 2018} % Date(s)
    

%---------------------------------------------------------
  \cvpresentation
    {B. Seymour, and K. Yagi. "Testing General Relativity with Black Hole-Pulsar Binaries," Fall College Science Scholar Symposium. Charlottesville, VA. (Poster)} % Role
    {Oct. 2018} % Date(s)


%---------------------------------------------------------

  \cvpresentation
    {B. Seymour, and K. Yagi. “Testing General Relativity with Black Hole-Pulsar Binaries,” Astronaut Scholarship Foundation Technical Conference. Washington DC. (Oral)} % Role
    {Aug. 2018} % Date(s)


%---------------------------------------------------------

  \cvpresentation
    {B. Seymour, M. Kasprzack, A. Pele, and A. Mullavey. “Non-Linear Angular Noise Coupling into Differential Arm Length,” UVa Sigma Pi Sigma Symposium. Charlottesville, VA. (Oral)} % Role
    {Nov. 2017} % Date(s)


%---------------------------------------------------------

  \cvpresentation
    {B. Seymour, M. Kasprzack, A. Pele, and A. Mullavey. “Characterization of Nonlinear Angular Noise Coupling into Differential Arm Length of the LIGO Livingston Detector,” LIGO SURF Session. Pasadena, CA. (Oral)} % Role
    {Aug. 2017.} % Date(s)


%---------------------------------------------------------

  \cvpresentation
    {B. Seymour, O. Cypull, C. O’Dea, S. Cheng, and K. Feitosa. “Stress Induced Rearrangements in a Bubble Raft,” SESAPS Conference. Charlottesville, VA. (Oral)} % Role
    {Nov. 2016} % Date(s)


%---------------------------------------------------------

  \cvpresentation
    {B. Seymour, O. Cypull, C. O’Dea, S. Cheng, and K. Feitosa. “Interfacial Bubble Deformations,” UVa Sigma Pi Sigma Symposium. Charlottesville, VA. (Poster)} % Role
    {Oct. 2016} % Date(s)


%---------------------------------------------------------

  \cvpresentation
    {B. Seymour, O. Cypull, S. Cheng, and K. Feitosa. “Stress Induced Rearrangements in a Bubble Raft,” JMU Summer Symposium. Harrisonburg, VA. (Oral)} % Role
    {Aug. 2016} % Date(s)


%---------------------------------------------------------

  \cvpresentation
    {B. Seymour, O. Cypull, S. Cheng, and K. Feitosa. “Interfacial Bubble Deformations,” 83rd Annual American Physical Society March Meeting. Baltimore, MD. (Poster)} % Role
    {Mar. 2016} % Date(s)


%---------------------------------------------------------

  \cvpresentation
    {B. Seymour, O. Cypull, and K. Feitosa. “Interfacial Bubble Deformations,” Third Annual Virginia Soft Matter Workshop. Charlottesville, VA. (Oral)} % Role
    {Nov. 2015} % Date(s)


%---------------------------------------------------------

  \cvpresentation
    {B. Seymour, O. Cypull, S. Cheng, and K. Feitosa. “Bubble Deformations at the Air-Water Interface,” JMU Summer Symposium. Harrisonburg, VA. (Oral)} % Role
    {Aug. 2015} % Date(s)


%---------------------------------------------------------

\end{cvpresentations}
